Ca exp analysis -- 4/18/2018

### 2018-04-28 resistingrhythm/analysis/burst_analysis.Rmd
Rmd vis - tweaks to nearly everything

```{r, message=FALSE}
exp_code <- 3
osc_codes <- c(0, 1, 3, 5)
osc_rates <- c(0.5, 1, 3, 5)
stim_codes <- c(0, 1, 2)

@@

    results <- rbind(results, df)
  }
}
```

@@

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Mod. rate (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_hline(yintercept=0, size=0.5) +
  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=kappa_coord)) +
  geom_point(size=0.4, alpha=0.2) + 
  theme_classic() + 
  labs(y="Kappa", x="Error") +
  facet_grid(.~osc_rate)
```

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var)) +
  geom_point(size=0.4, alpha=0.2) + 
  theme_classic() + 
  labs(y="Variance", x="Error") +
  facet_grid(.~osc_rate)
```

>>>>

```{r, message=FALSE}

exp_code <- 16
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

@@

    results <- rbind(results, df)
  }
}

# exp_code <- 3
# osc_codes <- c(0, 1, 3, 5)
# osc_rates <- c(0.5, 1, 3, 5)
# stim_codes <- c(0, 1, 2)
# 
# results0 <- NULL
# for(i in 1:length(osc_codes)){
#   for(s_c in stim_codes){
#     o_c <- osc_codes[i]
#     o_r <- osc_rates[i]
#     
#     # Load the csv
#     df <- read_csv(paste(data_path, 
#                          "exp", as.character(exp_code), 
#                          "_stim", as.character(s_c), 
#                          "_burst", as.character(o_c),
#                          ".csv", sep=""))
#     
#     # Add metadata
#     df$osc_code <- rep(o_c, nrow(df))
#     df$osc_rate <- rep(o_r, nrow(df))
#     df$stim_code <- rep(s_c, nrow(df))
#     
#     results0 <- rbind(results0, df)
#   }
# }
# 
# 
# exp_code <- 14
# osc_codes <- c(7, 8, 9, 10, 11, 12, 13, 14, 15)
# osc_rates <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45)
# stim_codes <- c(0, 1, 2)
# 
# results1 <- NULL
# for(i in 1:length(osc_codes)){
#   for(s_c in stim_codes){
#     o_c <- osc_codes[i]
#     o_r <- osc_rates[i]
#     
#     # Load the csv
#     df <- read_csv(paste(data_path, 
#                          "exp", as.character(exp_code), 
#                          "_stim", as.character(s_c), 
#                          "_burst", as.character(o_c),
#                          ".csv", sep=""))
#     
#     # Add metadata
#     df$osc_code <- rep(o_c, nrow(df))
#     df$osc_rate <- rep(o_r, nrow(df))
#     df$stim_code <- rep(s_c, nrow(df))
#     
#     results1 <- rbind(results1, df)
#   }
# }
# 
# results0 %>% 
#   select(k, osc_rate, osc_code, kappa_error, kappa_coord, mse_error, 
#          mse_var, abs_error, abs_var, rate_k, rate_ref, stim_code) -> results0
# results1 %>% 
#   select(k, osc_rate, osc_code, kappa_error, kappa_coord, mse_error, mse_var, abs_error, abs_var, rate_k, rate_ref, stim_code) -> results1
# results <- rbind(results0, results1)

results %>% 
  filter(kappa_coord > 0) -> results
```

@@

```{r, fig.width=2.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=3.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  # geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Mod. rate (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_hline(yintercept=0, size=0.5) +
  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=kappa_coord)) +
  geom_point(size=0.4, alpha=0.2) + 
  geom_smooth(method='lm', color="red", alpha=0.4, se=FALSE, size=0.1) +
  theme_classic() + 
  labs(y="Kappa", x="Error") +
  facet_grid(.~osc_rate)
```

```{r, fig.width=2.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var)) +
  geom_point(size=0.4, alpha=0.2) + 
  geom_smooth(method='lm', color="red", alpha=0.4, se=FALSE, size=0.1) +
  theme_classic() + 
  labs(y="Variance", x="Error") +
  facet_grid(.~osc_rate)
```

### 2018-04-28 resistingrhythm/analysis/ca_analysis_v2.Rmd
Rmd vis - tweaks to nearly everything

```{r, message=FALSE}
exp_code <- 1
osc_codes <- c(1, 3, 5)
osc_rates <- c(1, 3, 5)
stim_codes <- c(0)

# Load exp 1 results for comparison

results <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$Ca_target <- rep("0.030", nrow(df))

    results <- rbind(results, df)
  }
}

# Rename Ca to match new format
results %>% 
  rename(Ca_obs_target = Ca_k) %>% 
  mutate(Ca_obs_ref = Ca_obs_target) -> results

# ------------------------------------------------------------------
# exp_code <- 2
# ca_values <- c("0.032", "0.034", "0.036", "0.038")

exp_code <- 7
ca_values <- c("0.032", "0.034", "0.036")
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_values){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Generate name
      file_name <- paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         "_Ca", ca,
                         ".csv", sep="")

      if (file.exists(file_name)){
        # Load
        df <- read_csv(file_name)

        # Add metadata
        df$osc_code <- rep(o_c, nrow(df))
        df$osc_rate <- rep(o_r, nrow(df))
        df$stim_code <- rep(s_c, nrow(df))

        results <- rbind(results, df)  
      }
    }
  }
}

@@

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```
```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Firing rate (Hz)", x="Rate (Hz") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=1.0}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_ref - rate_k, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_hline(yintercept=0, size=0.5) +
  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.2, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=kappa_coord, color=Ca_target)) +
  geom_point(alpha=0.5, size=0.2) + 
  theme_classic() + 
  labs(y="Kappa", x="Error") +
  facet_grid(.~osc_rate)
```

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var, color=Ca_target)) +
  geom_point(alpha=0.5, size=0.2) + 
  theme_classic() + 
  labs(y="Variance", x="Error") +
  facet_grid(.~osc_rate)
```

>>>>

```{r, message=FALSE}
exp_code <- 19
osc_codes <- c(101, 103, 105, 115, 125, 135, 145, 155)
osc_rates <- c(0.1, 0.3, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(0, 1)

ca_targets <- c(0.026, 0.028, 0.032, 0.034)

results <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      df <- read_csv(paste(data_path,
                           "exp", as.character(exp_code),
                           "_stim", as.character(s_c),
                           "_osc", as.character(o_c),
                           "_ca", as.character(ca),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))

      results <- rbind(results, df)
    }
  }
}

# exp_code <- 1
# osc_codes <- c(1, 3, 5)
# osc_rates <- c(1, 3, 5)
# stim_codes <- c(0)
# 
# # Load exp 1 results for comparison
# 
# results <- NULL
# for(i in 1:length(osc_codes)){
#   for(s_c in stim_codes){
#     o_c <- osc_codes[i]
#     o_r <- osc_rates[i]
#     
#     # Load the csv
#     df <- read_csv(paste(data_path, 
#                          "exp", as.character(exp_code), 
#                          "_stim", as.character(s_c), 
#                          "_osc", as.character(o_c),
#                          ".csv", sep=""))
#     
#     # Add metadata
#     df$osc_code <- rep(o_c, nrow(df))
#     df$osc_rate <- rep(o_r, nrow(df))
#     df$stim_code <- rep(s_c, nrow(df))
#     df$Ca_target <- rep("0.030", nrow(df))
#     
#     results <- rbind(results, df)
#   }
# }
# 
# # Rename Ca to match new format
# results %>% 
#   rename(Ca_obs_target = Ca_k) %>% 
#   mutate(Ca_obs_ref = Ca_obs_target) -> results
# 
# # ------------------------------------------------------------------
# # exp_code <- 2
# # ca_values <- c("0.032", "0.034", "0.036", "0.038")
# 
# exp_code <- 7
# ca_values <- c("0.032", "0.034", "0.036")
# for(i in 1:length(osc_codes)){
#   for(s_c in stim_codes){
#     for(ca in ca_values){
#       o_c <- osc_codes[i]
#       o_r <- osc_rates[i]
#       
#       # Generate name
#       file_name <- paste(data_path, 
#                          "exp", as.character(exp_code), 
#                          "_stim", as.character(s_c), 
#                          "_osc", as.character(o_c),
#                          "_Ca", ca,
#                          ".csv", sep="")
#     
#       if (file.exists(file_name)){
#         # Load
#         df <- read_csv(file_name)
# 
#         # Add metadata
#         df$osc_code <- rep(o_c, nrow(df))
#         df$osc_rate <- rep(o_r, nrow(df))
#         df$stim_code <- rep(s_c, nrow(df))
#         
#         results <- rbind(results, df)  
#       }
#     }
#   }
# }

@@

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  facet_grid(.~Ca_target) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```
```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  facet_grid(.~Ca_target) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error/1e3, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  facet_grid(.~Ca_target) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  facet_grid(.~Ca_target) +
  labs(y="Mod. rate (Hz)", x="Rate (Hz") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=1.0}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k - rate_ref, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  facet_grid(.~Ca_target) +
  labs(y="Delta rate (Hz)", x="Rate (Hz)") +
  theme_classic() 
```

@@

```{r, fig.width=2, fig.height=2}
results %>% 
  ggplot(aes(x=mse_error/1e3, y=mse_var, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  facet_grid(Ca_target~.) +
  labs(y="Variance", x="Error") +
  theme_classic() 
```
